Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-02-28 paper.tex
changes until the beginning of section 3

Models are very important for sciences and engineering that employs it to analyze, predict and design the behavior of modeled systems. Specially, deterministic and stochastic model are the basis of the major part of engineering advances for the last centuries. However, these models are not enough to represent CPS because the convergence between software, communications and hardware present a lot of events that could not be deterministically or stochastically modeled, and are better represented by nondeterministic models~\cite{leeCPS15}.

The early representation of hybrid systems, {\it i.e.} systems that mixes continuous and discrete dynamics, consists in representing the discrete components and discretized continuous dynamics using discrete models, considering the non-modeled effects as uncertainties or perturbations exogenous to the models. This approach is not suitable for complex CPS that presents a lot of nondeterminism.

CPS have been modeled through different structures that present different degrees of nondeterminism and proportion between continuous and discrete dynamics, e.g., timed automata (\textcolor{red}{CITAR}) and hybrid automata (\textcolor{red}{CITAR}). Rungger and Tabuada (\textcolor{red}{CITAR TAC 2016}) proposed a general and wide model for CPS. Following this proposal, a CPS $S$ is a tuple $S=(X,X_{0},U,r)$, where $X$ is a set of reachable states, $X_{0}$ is a set of initial states, $U$ is a set of inputs, and $r$ is a transition function, such that $r:X\times U \rightarrow X$.

@@

In general, BMC techniques aim to check the violation of a given (safety) property at a given system depth, as shown in Figure~\ref{bounded-model-checking}. Indeed, given a transition system \textit{M}, which is derived from the control-flow graph of a program, a property $\phi$, which represents the program correctness and/or the system's behavior, and an iteration bound \textit{k}, which limits the loop unrolling, data structures, and context-switches, BMC techniques thus unfold a system \textit{k} times, in order to convert it into a verification condition $\psi$, expressed in propositional logic or in a decidable-fragment of first-order logic, such that $\psi$ is \textit{satisfiable} if and only if $\phi$ has a counterexample of depth less than or equal to \textit{k}.

>>>>

Models are largely employed in the science and engineering areas, in order to analyze, predict and modify the behavior of real-world systems. Specially, deterministic and stochastic models are the basis of many engineering advances, in the last centuries. The former is uniquely determined by parameter values and previous states, while the latter presents inherent randomness, which is described by probability distributions. Nonetheless, one can argue that such models are not enough to represent CPSs, because the interaction among software, communications, and hardware presents a lot of events that could not be deterministically or stochastically modeled and may be better represented by nondeterministic approaches~\cite{leeCPS2}. Indeed, that is even more evident when unknown properties are addressed, such as human behavior.

On the one hand, the early representation of hybrid systems, {\it i.e.}, systems that mix continuous and discrete dynamics, consisted in representing discrete components and discretized continuous dynamics by using discrete models and considering non-modeled effects as uncertainties or perturbations exogenous to them, which may even be negligible. On the other hand, that approach is not suitable for complex CPSs that present a lot of nondeterminism, given that uncertainties play a central role.

CPSs have been modeled through different structures that present different degrees of nondeterminism and balance between continuous and discrete dynamics, such as timed automata (\textcolor{red}{CITAR}) and hybrid automata (\textcolor{red}{CITAR}). Rungger and Tabuada (\textcolor{red}{CITAR TAC 2016}) proposed a general and wide model for CPS. Following this proposal, a CPS $S$ is a tuple $S=(X,X_{0},U,r)$, where $X$ is a set of reachable states, $X_{0}$ is a set of initial states, $U$ is a set of inputs, and $r$ is a transition function, such that $r:X\times U \rightarrow X$.

\textcolor{red}{seria legal falar que nondeterminism pode ser tratado com model checking}

@@

In general, BMC techniques aim to check the violation of a given (safety) property at a given system depth, as shown in Figure~\ref{bounded-model-checking}. Indeed, given a transition system \textit{M}, which is derived from the control-flow graph of a program, a property $\phi$, which represents program correctness and/or a system's behavior, and an iteration bound \textit{k}, which limits loop unrolling, data structures, and context-switches, BMC techniques thus unfold a system \textit{k} times, in order to convert it into a verification condition $\psi$, which is expressed in propositional logic or in a decidable-fragment of first-order logic, such that $\psi$ is \textit{satisfiable} if and only if $\phi$ has a counterexample of depth less than or equal to \textit{k}.
